DraftFunctions

### 2022-02-07 R/DraftFunctions.Rmd
Clean after 2ndTrails

>>>>

# Secondary trails in Data
```{r}
scenario <- "manual"
winching <- "2"
objective <- 10
fuel <- "2"
diversification <- TRUE

inventory <- addtreedim(cleaninventory(Paracou6_2016, PlotMask),
                        volumeparameters = ForestZoneVolumeParametersTable)

treeselectionoutputs <- suppressWarnings(treeselection(inventory,
                                                       topography = DTMParacou,
                                                       speciescriteria = SpeciesCriteria, objective = objective,
                                                       scenario = "manual", fuel = fuel,
                                                       diversification = diversification,
                                                       winching = winching, specieslax = FALSE,
                                                       objectivelax = TRUE, plotslope = HarvestableAreaOutputsCable$PlotSlope,
                                                       harvestablepolygons = HarvestableAreaOutputsCable$HarvestablePolygons,
                                                       advancedloggingparameters = loggingparameters()))

SecondaryTrails <- secondtrailsopening(
  topography = DTMParacou,
  plotmask = PlotMask,
  maintrails = MainTrails,
  plotslope = HarvestableAreaOutputsCable$PlotSlope,
  harvestablepolygons = HarvestableAreaOutputsCable$HarvestablePolygons,
  machinepolygons = HarvestableAreaOutputsCable$MachinePolygons,
  treeselectionoutputs = treeselectionoutputs,
  CostMatrix = list(list(list(Slope = 3, Cost = 3),
                         list(Slope = 5, Cost = 5),
                         list(Slope = 12, Cost = 20),
                         list(Slope = 22, Cost = 60),
                         list(Slope = 35, Cost = 1000),
                         list(Slope = Inf, Cost = Inf)),
                    list(list(CostType = "Initial", CostValue = 1000),
                         list(CostType = "Access", CostValue = Inf),
                         list(CostType = "BigTrees", CostValue = 500),
                         list(CostType = "Reserves", CostValue = 500),
                         list(CostType = "Futures", CostValue = 50),
                         list(CostType = "MainTrails", CostValue = 1E-4),
                         list(CostType = "SecondTrails", CostValue = 0.1))),
  scenario = "manual",
  winching = winching,
  advancedloggingparameters = loggingparameters())

# usethis::use_data(SecondaryTrails, overwrite = TRUE)
```
